Hadi Esmaeilzadeh is awarded early tenure at UC San Diego, where he is the inaugural holder of Halicioglu Chair in Computer Architecture with the rank of full professor in Computer Science and Engineering. Before UC San Diego, he was an assistant professor in the School of Computer Science at Georgia Tech. There, he was the inaugural holder of the Allchin Family Early Career Professorship. Dr. Esmaeilzadeh obtained his Ph.D. in Computer Science and Engineering from the University of Washington in 2013. His Ph.D. work received the 2013 William Chan Memorial Best Dissertation Award.  He is the founding director of the Alternative Computing Technologies (ACT) Lab, where his team is developing new technologies and cross-stack solutions to enable responsible immersive intelligence.\\
His research has been recognized by four ISCA-50 Retrospective, highlighting the four of his papers’ significance over the past 25 years of ISCA from 1996 through 2020. Prof. Esmaeilzadeh’s work has also been recognized by four Communications of the ACM Research Highlights, four IEEE Micro Top Picks, a nomination for Communications of the ACM Research Highlights, an honorable mention in IEEE Micro Top Picks, and a Distinguished Paper Award in HPCA 2016. Hadi’s work on dark silicon has also been profiled in The New York Times.\\
Prof. Esmaeilzadeh received the IEEE Technical Committee on Computer Architecture (TCCA) “Young Architect” Award in 2018 and was inducted into the ISCA Hall of Fame in the same year.  He has also received the Air Force Office of Scientific Research Young Investigator Award (2017), 
Google Research Faculty Award (2024, 2018, 2016 and 2014), Samsung Research Award (2024 and 2023), Qualcomm Research Award (2020, 2017, and 2016), Microsoft Research Award (2017 and 2016),
College of Computing Outstanding Junior Faculty Research Award (2017), and Lockheed Inspirational Young Faculty Award (2016).
More information is available on his webpage, \url{https://cseweb.ucsd.edu/~hadi/}
